Maps

### 2020-04-26 ms_8.Rmd
Commit with working map tab

```{r testModel}
#
# model1 <- lm(data = mwdata, perc_school ~ state + land_in_farms)
```

@@

saveRDS(clean_data, file = "final/my_data.rds")
saveRDS(clean_data, file = "my_data.rds")

@@

```{r mapDataset}

@@

@@

```{r shapefiles}

@@

```{r gisTemplate}
# might also want to add a filter for state??
# if time permits...

# gis template for any year/variable desired
# only change these two lines!
year <- 1870
myvar <- "Average Farm Value"

#choices for myvar will be determined by: 
appPlan <- allData %>%
  filter(YEAR == "1870") %>%
  select_if(~ !all(is.na(.))) %>%
  select(-STATEA:-COUNTY) %>%
  select(-multiplier)

@@

```{r experimentalModels}

@@

```{r farmTrends}
# this takes foever--cache it

@@

>>>>

@@

saveRDS(clean_data, file = "final/my_data.rds")
saveRDS(clean_data, file = "my_data.rds")
saveRDS(clean_data, file = "testing123/my_data.rds")

@@

```{r mapDataset, cache=TRUE}

@@

saveRDS(mwData, file = "final/mwData.rds")

@@

```{r shapefiles, cache=TRUE}

@@

```{r gisTemplate, cache=TRUE}
# might also want to add a filter for state??
# if time permits...

# gis template for any year/variable desired
# only change these two lines!
year <- 1950

#choices for myvar will be determined by: 
appPlan <- mwData %>%
  filter(YEAR == year) %>%
  select_if(~ !all(is.na(.))) %>%
  select(-STATEA:-COUNTY)

# myvar options will be determined by column names of appPlan & displayed via dropdown widget
myvar <- "Irrigated Acres"

@@

```{r experimentalModels, eval = FALSE}

@@

```{r farmTrends, eval = FALSE}
# this takes foever--cache it

@@

tabPanel("Maps",

                                 pageWithSidebar(

                                     headerPanel("Midwest Map Explorer"),

                                     sidebarPanel(
                                         uiOutput("choose_dataset"),

                                         uiOutput("choose_columns"),
                                         br(),
                                         a(href = "https://gist.github.com/4211337", "Source code")
                                     ),

                                     mainPanel(
                                         tabsetPanel(id = "tabsMain",
                                                     tabPanel("Map",
                                         leafletOutput("map1")
                                     ),
                                     tabPanel("Interesting Observations",
                                              # Don't write in the first p()
                                              # Looks bad
                                              p(""),
                                              p("Write some stuff!")))
                                 ))),
